---
title: "Heirarchical Clustering"
author: "Anastasia Kunz"
date: "3/2/2021"
output:
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(here)
library(janitor)
library(NbClust)
library(cluster)
library(factoextra)
library(dendextend)
library(ggdendro)
```

## Water Chemistry Cluster Analysis

```{r}
# Read in data
stream_chem <- read_csv(here("data", "sbc_lter_registered_stream_chemistry.csv"))

stream_chem[stream_chem == -999.0] <- NA


```

```{r}

# some wrangling; group by site and calculate average for each water chemistry metric

site_avgs <- stream_chem %>% 
  group_by(site_code) %>% 
  summarize(nh4_um_av = mean(nh4_uM, na.rm = TRUE),
            no3_um_av = mean(no3_uM, na.rm = TRUE),
            po4_um_av = mean(po4_uM, na.rm = TRUE),
            tdn_um_av = mean(tdn_uM, na.rm = TRUE),
            tdp_um_av = mean(tdp_uM, na.rm = TRUE),
            tpc_um_av = mean(tpc_uM, na.rm = TRUE),
            tpn_um_av = mean(tpn_uM, na.rm = TRUE),
            tpp_um_av = mean(tpp_uM, na.rm = TRUE),
            tss_mgL_av = mean(tss_mgperLiter, na.rm = TRUE),
            spec_cond_av = mean(spec_cond_uSpercm, na.rm = TRUE)) %>% 
  na.omit()
  
# omit na, and scale variables
streams_scaled <- site_avgs %>% 
  select(2:11) %>% 
  scale()

#attach rownames to the scaled dataset
rownames(streams_scaled) <- site_avgs$site_code

#calculate euclidean
euclid_dist <- dist(streams_scaled, method = "euclidean")

# Heirarchical Clustering through Complete Linkage:
hclust_complete <- hclust(euclid_dist, method = "complete")


```

#### Dendrogram of Stream Site Cluster Analysis

```{r, fig.cap= "**Figure 1.** Hierarchical cluster analysis by complete linkage of nine stream sites in Santa Barbara coastal drainage."}
ggdendrogram(hclust_complete) +
  theme_minimal() +
  labs(x = "Stream Site Code",
       y = " ",
       title = "Hierarchical Cluster Analysis of Stream Chemistry")+
  theme(panel.grid.major = element_blank())
```




## Citation

SBC LTER: Stream chemistry in the Santa Barbara Coastal drainage area, ongoing since 2000
Creators: Santa Barbara Coastal LTER, & Melack, John M
Citation: Santa Barbara Coastal LTER and J. Melack. 2019. SBC LTER: Land: Stream chemistry in the Santa Barbara Coastal drainage area, ongoing since 2000 ver 16. Environmental Data Initiative. https://doi.org/10.6073/pasta/67a558a24ceed9a0a5bf5e46ab841174. 

