---
title: "Exclusionary Analysis using Bootstrapping"
author: "Anastasia Kunz"
date: "3/2/2021"
output:
  html_document:
    theme: flatly
    code_folding: hide
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(here)
library(boot)
library(gt)
library(broom)
```

## Exclusionary Conduct Bootstrapped Analysis

```{r}
# create vector of "yes" reported exclusionary experiences (1) or "no" did not report exclusionary experiences (0)
excluded <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0)

# create function to calculate proportion: need to add all up and divide by 36
proportion_fun <- function (x,i) {sum(x[i])/36}

# bootstrap 100,000
boot_100k <- boot(excluded,
                 statistic = proportion_fun,
                 R = 100000)
tidy_boot <- broom::tidy(boot_100k)

# create data frame
exclude_100k <- data.frame(prop = boot_100k$t)

# plot
ggplot(data = exclude_100k, aes(x = prop))+
  geom_histogram()+
  theme_classic()+
  labs(
    x = "Proportion",
    y = "Count",
    title = "Exclusionary Experiences Among Nonbinary or Genderqueer Students"
  )

```

```{r}
# get confidence interval
confidence <-boot.ci(boot_100k, conf = 0.95)

# I want to know the mean of the bootstrapped proportions
tidy_boot_avg <- tidy_boot %>%
  mutate(mean = mean(boot_100k$t))
  

```

According to this analysis using bootstrapping, an average of `r round(tidy_boot_avg[4]*100, 2)`% (n = 36, n = 100,000 bootstrap samples) of genderqueer students reported exclusionary experiences, with a confidence interval of [44.44, 77.78]. The bootstrapped results had a bias of `r format(as.character(round(tidy_boot_avg[2],4)), scientific = TRUE)` and a standard error of `r round(tidy_boot_avg[3], 3)`.

```{r}
tidy_boot_avg %>% 
  gt() %>% 
  fmt_percent(
    columns = vars(statistic, mean),
    decimals = 2
  ) %>% 
  fmt_number(
    columns = vars(bias),
    decimals = 5
  ) %>% 
  fmt_number(
    columns = vars(std.error),
    decimals = 3
  ) %>% 
  tab_options(
    table.width = pct(60)
  ) %>% 
  tab_header(
    title = "Bootstrap Results"
  ) %>% 
  cols_label(
    statistic = "Statistic",
    bias = "Bias",
    std.error = "Standard Error",
    mean = "Bootstrap Average"
  )
```




### Data Citation

UCSB Campus Climate Project Final Report 2014. Prepared by Rankin & Associates Consulting, available at http://campusclimate.ucop.edu/_common/files/pdf-climate/ucsb-full-report.pdf