---
title: "Wild Fish Catch"
author: "Anastasia Kunz"
date: "3/2/2021"
output:
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(here)
library(janitor)
library(nlstools)
library(tsibble)
library(lubridate)
```


## Wild Fish Catch Analysis

Breif blurb about wild fish catch.

```{r}
fish_catch <- read_csv(here("data", "fish_catch.csv"), skip = 4) %>% 
  select(X1, X2) %>% 
  rename(year = X1,
         wild_catch = X2) %>% 
  head(-4) %>% 
  mutate(year = as.numeric(year))

```

### Data Exploration: Wild Fish Catch Time Series

```{r}
# make time series of fish catch
ggplot(fish_catch, aes(x = year, y = wild_catch))+
  geom_line()+
  theme_minimal()+
  labs(
    x = "Year",
    y = "Fish Catch (Million Tons)",
    title = "Global Wild Fish Catch",
    subtitle = "1950 - 2012"
  )
```

Can see a general increasing trend through time, which looks roughly like logistic growth.

Therefore, we will use $P(t)=\frac{K}{1+Ae^{-kt}}$  and estimate our parameters based off of the graph above.

**K Estimate**

Wild fish catch levels off around 1990, at about 90 to 95 million tons of wild fish catch per year. *So the estimate for K will be 95 million tons.*


**k Estimate**

We can estimate *k* by looking at the log of wild fish catch pre 1990 to find the growth rate. *Here we estimate it as 0.036.*

```{r}
fish_exp <- fish_catch %>% 
  filter(year < 1985) %>% 
  mutate(ln_fish = log(wild_catch))

lm_fish <- lm(ln_fish ~ year, data = fish_exp)

```


**A Estimate**
Based on our equation where $A$ = $\frac{K-P_0}{P_0}$ we can estimate A to be $\frac{95 - 5}{5}$ = *about 18.*



```{r}
#df_nls <- nls(pop ~ K/(1 + A*exp(-r*time)),
   #           data = df,
   #           start = list(K = 180, A = 17, r = 0.17),
   #           trace = TRUE
   #           )
```





### Data Citation 
Global wild fish catch and aquaculture production, compiled by Earth Policy Institute with 1950-2010 from U.N. Food and Agriculture Organization (FAO), Global Capture Production and Global Aquaculture Production, electronic databases, at www.fao.org/fishery/topic/16140/en.
